DOpElib: Differential Equations and Optimization Environment; A Goal Oriented Software Library for Solving PDEs and Optimization Problems

### 2012-11-26 Paper_May_2012/main.tex
Frage von mir mit Christian geklaert und entsprechender Formulierungsvorschlag eingebaut.

Now we may discretize the problem with some time-stepping scheme, which will 
remove the temporal derivative and replace it by some difference quotients. 
Since the exact way of doing this depends on the time-stepping scheme 
we need a new object that takes the user-given description of the PDE and 
generates the appropriate combinations of spatial integrals and scaling.
Thus a generic problem may look as follows:
\begin{lstlisting}
  template<typename PROBLEM>
      class TimeStepProblem(Problem & P);
\end{lstlisting}
At present we have prepared the following time-stepping schemes in \dope:
\begin{itemize}
\item Forward-(or Explicit)-Euler
\item Backward-(or Implicit)-Euler
\item Crank-Nicolson scheme
\item shifted Crank-Nicolson scheme (to deal with singular initial data)
\item fractional-step-$\theta$ scheme
\end{itemize}
\todo{CG and WW: bitte pruefen}
After choosing the time-stepping scheme, the SpaceTimeHandler  
loops over all time-steps, where in each of the 
time-steps we can reuse the functionality \todocg{we employed} to solve stationary PDEs.\todocg{Hier Beispiele, was genau wir wiederverwenden? Oder auf den naechsten Abschnitt verweisen?} 
Now it is apparent, why we introduced the \texttt{StatPDEProblem}, because
we define the \texttt{InstatPDEProblem} to contain the necessary 
loop over all time points. Consequently, the implementation 
of nonstationary problems is quite similar to stationary problems,
which was one major goal we claimed at the beginning.
Next, we will describe the methods (i.e., changes) the user needs to 
provide in addition to the stationary case.

>>>>

Now we may discretize the problem with some time-stepping scheme, which will 
remove the temporal derivative and replace it by some difference quotients. 
Since the exact way of doing this depends on the time-stepping scheme 
we need a new object that takes the user-given description of the PDE and 
generates the appropriate combinations of spatial integrals and scaling.
Thus a generic problem may look as follows:
\begin{lstlisting}
  template<typename PROBLEM>
      class TimeStepProblem(Problem & P);
\end{lstlisting}
At present we have prepared the following time-stepping schemes in \dope:
\begin{itemize}
\item Forward-(or Explicit)-Euler
\item Backward-(or Implicit)-Euler
\item Crank-Nicolson scheme
\item shifted Crank-Nicolson scheme (to deal with singular initial data)
\item fractional-step-$\theta$ scheme
\end{itemize}
\todo{bitte gegenlesen}
After choosing the time-stepping scheme, the SpaceTimeHandler  
loops over all time-steps, where in each of the 
time-steps we can reuse the functionality we have provided to solve 
stationary PDEs. 
This means for instance, if we have implemented the 
cell-integrals in the weak formulation for the stationary case, 
then we can use the exact same 
implementation again for the solution of the nonstationary version of 
the equation. However, we will possibly need to provide an additional 
term to cope with the integral for the time derivative.

Now it is apparent, why we introduced the \texttt{StatPDEProblem}, because
we define the \texttt{InstatPDEProblem} to contain the necessary 
loop over all time points. Consequently, the implementation 
of nonstationary problems is quite similar to stationary problems,
which was one major goal we claimed at the beginning.
Next, we will describe the methods (i.e., changes) the user needs to 
provide in addition to the stationary case.
